---
output: flexdashboard::flex_dashboard
runtime: shiny
---

```{r}

library(flexdashboard)
library(PerformanceAnalytics)
library(quantmod)
library(dygraphs)

monthly_stock_returns <- function(ticker, start_year)
{
  symbol <- getSymbols(ticker, src = 'yahoo', from = start_year, auto.assign = FALSE,
                       warnings = FALSE)
  data <- periodReturn(symbol, period = 'monthly', type = 'log')
  colnames(data) <- as.character(ticker)
  assign(ticker, data, .GlobalEnv)
}

```


Inputs {.sidebar}
======================
```{r}
helpText("Choose 3 stocks and their % allocation")

# helpText() Prints to dashboard
# fluidRow() generates a row containing inputs
# column() generates column-width for input
# textInput(varname, DashboardName, Default)
# numericInput(varname, DashboardName, Default, constraints)

fluidRow(
  column(7,
  textInput("stock1", "Stock 1", "GOOG")),
  column(5,
  numericInput("w1", "Portf. %", 25, min = 1, max = 100))
)

fluidRow(
  column(7,
  textInput("stock2", "Stock 2", "FB")),
  column(5,
  numericInput("w2", "Portf. %", 25, min = 1, max = 100))
)


fluidRow(
  column(7,
  textInput("stock3", "Stock 3", "AMZN")),
  column(5,
  numericInput("w3", "Portf. %", 25, min = 1, max = 100))
)

helpText("Choose a start date and risk-free rate")


fluidRow(
  column(7,
  dateInput("year", "Starting Date", "2010-01-01", format = "yyyy-mm-dd")),
  column(5,
  numericInput("rfr", "Risk-free %", .5, min = 0, max = 5, step = 0.01))
)

actionButton("go", "Submit")
```


```{r}
individual_stocks <- reactive({
  year <- input$year
  req(input$stock1)
  stock1 <- monthly_stock_returns(input$stock1, year)
  req(input$stock2)
  stock2 <- monthly_stock_returns(input$stock2, year)
  req(input$stock3)
  stock3 <- monthly_stock_returns(input$stock3, year)
  
  merged_returns <- merge.xts(stock1, stock2, stock3)
})


#individual_stocks <- eventReactive(input$go, {
#  year <- input$year
#  req(input$stock1)
#  stock1 <- monthly_stock_returns(input$stock1, year)
#  req(input$stock2)
#  stock2 <- monthly_stock_returns(input$stock2, year)
#  req(input$stock3)
#  stock3 <- monthly_stock_returns(input$stock3, year)
  
#  merged_returns <- merge.xts(stock1, stock2, stock3)
#})

portfolio_growth <- reactive({
  w <- c(input$w1/100, input$w2/100, 1-(input$w1+input$w2)/100)
  dollar_growth <- Return.portfolio(individual_stocks(), weights = w, wealth.index = TRUE)
})
  
sharpe_ratio <- reactive({
  w1 <- c(input$w1/100, input$w2/100, 1-(input$w1+input$w2)/100)
  portfolio_monthly_returns <- Return.portfolio(individual_stocks(), weights = w1)
  
  sharpe <- round(SharpeRatio(portfolio_monthly_returns, Rf = input$rfr/100), 4)
  sharpe[1,]
})

sp500_sharpe_ratio <- reactive({
  year <- input$year
  sp500 <- monthly_stock_returns('spy', year)
  sp500_monthly <- Return.portfolio(sp500)
  sp500_sharpe <- round(SharpeRatio(sp500_monthly, Rf = input$rfr/100), 4)
})

```


Portfolio Performance
===========================

Row {data-height = 600}
---------------------------

### Growth of $1

```{r}
dygraphOutput("dygraphDollarGrowth")

output$dygraphDollarGrowth <- renderDygraph({
  dygraph(portfolio_growth(), main = "Growth of $1 Invested in Your Portfolio") %>%
    dyAxis("y", label = "$") %>%
    dyOptions(axisLineWidth = 1.5, fillGraph = TRUE, drawGrid = TRUE)
})
```

Row {data-height = 200}
-----------------------------

### The Sharpe Ratio of Your Portfolio

```{r}
valueBoxOutput("approvalBox1")
output$approvalBox1 <- renderValueBox({
  valueBox(value = sharpe_ratio(), icon = 'fa-line-chart', color = "primary")
})
```

### Sharpe Ratio of S&P500 in the same time period

```{r}
valueBoxOutput("approvalBox2")
output$approvalBox2 <- renderValueBox({
  valueBox(value = sp500_sharpe_ratio(), icon = 'fa-line-chart', color = "primary")
})
```

Row {data-height=350}

----------------

### Background of the Sharpe Ratio

The Sharpe ratio was developed by Nobel laureate William F. Sharpe and is used to help investors understand the return of an investment compared to its risk. The ratio is the average return earned in excess of the risk-free rate per unit of volatility or total risk.

Subtracting the risk-free rate from the mean return allows an investor to better isolate the profits associated with risk-taking activities. Generally, the greater the value of the Sharpe ratio, the more attractive the risk-adjusted return.
